Creating the ``r params$package_name`` R package

### 2025-07-11 create-FSHybridPLS.Rmd
code: new version of get_xi_direct validated
same as the old version of get_xi_direct!

@@

xi_hat_lin <- get_xi_hat_linear(W, y)

# Wrap into predictor_hybrid object using format template
xi_hat_direct <- predictor_hybrid_from_coef(format = W_template, coef = xi_hat_lin)

>>>>

### helper: get_xi_hat_linear
```{r}
get_xi_hat_linear_new <- function(W, y){
  n <- W$n_sample
  K <- W$n_functional
  normalizer <- 0
  d = list()
  for (i in 1:K){  ## tPhi_tC : C multiplied by Phi. Scalable to arbitrary K
    Theta_t <- W$functional_list[[i]]$coefs
    B <- W$gram_list[[i]]
    d[[i]] <- Theta_t %*% y
    normalizer <- normalizer + t(y) %*% t(Theta_t) %*% B %*% Theta_t %*% y
  }
  d[[K+1]] <- t(W$Z) %*% y
  normalizer <- normalizer+ t(y) %*% W$Z %*% t(W$Z) %*% y
  d_vec <- do.call(c, d)  # or: unlist(d)
  d_vec <- d_vec/ sqrt(normalizer)
  return(d_vec)
}
```

compare xi_hat_lin, xi_hat_lin_new

@@

xi_hat_lin <- get_xi_hat_linear(W, y)
xi_hat_lin_new <- get_xi_hat_linear_new(W, y)
# Wrap into predictor_hybrid object using format template
xi_hat_direct <- predictor_hybrid_from_coef(format = W_template, coef = xi_hat_lin)
norm_val <- sqrt(inprod.predictor_hybrid(xi_hat_direct))
xi_hat_direct <- scalar_mul.predictor_hybrid(xi_hat_direct,  1 / norm_val)
xi_hat_direct_new <- predictor_hybrid_from_coef(format = W_template, coef = xi_hat_lin_new)

cat(xi_hat_direct_new$functional_list[[1]]$coefs- xi_hat_direct$functional_list[[1]]$coefs)
cat(xi_hat_direct_new$functional_list[[2]]$coefs- xi_hat_direct$functional_list[[2]]$coefs)

xi_hat_lin <- get_xi_hat_linear(W, y)
xi_hat_lin_new <- get_xi_hat_linear_new(W, y)
# Wrap into predictor_hybrid object using format template
xi_hat_direct <- predictor_hybrid_from_coef(format = W_template, coef = xi_hat_lin)
xi_hat_direct_new <- predictor_hybrid_from_coef(format = W_template, coef = xi_hat_lin_new)
